A Sound Deep Embedding of Arbitrary Normal Modal Logics in Coq

### 2022-08-31 paper/paper.tex
Adding acknolegments
Merge and fix acknowledgements

Before defining the Kripke semantics, we need to represent the model used to
interpret a modal logic formula. We encode a frame by a record formed by
a type \mintinline{coq}{W: Set} to represent the set of worlds and an
accessibility relation denoted by a type \mintinline{coq}{R: W -> W -> Prop}.
\begin{minted}{coq}
Record Frame: Type := {
  W: Set;
  R: W -> W -> Prop;
}.
\end{minted}
A model is then denoted by another record, formed by a frame and a labeling function,
which assign the truth value of a variable at a given world.
\begin{minted}{coq}
Record Model: Type := {
  F: Frame; 
  v: nat -> (W F) -> Prop; 
}.
\end{minted}
Note that the type of the labeling function \mintinline{coq}{v} ensures that it
refers to a world from the set of possible worlds in the frame
\mintinline{coq}{F} (we recall that \mintinline{coq}{W F} is Coq's syntax for
accessing field \mintinline{coq}{W} from the record \mintinline{coq}{F}). The encoding of the Kripke semantics is done by a Coq function
that implements the relation of Figure~\ref{fig:kripke}. We omit the code
for propositional logics connectives for brevity. The interesting parts are for
variables (constructor \mintinline{coq}{Lit}) which uses the labeling function
\mintinline{coq}{v} from the model \mintinline{coq}{M}. The meaning of
modalities $\Box$ and $\Diamond$ are represented by a quantifying over worlds
using the accessibility relation $R$. 
\begin{minted}{coq}
Fixpoint formula_valuation (M: Model) (w: W (F M))
                                 (phi: form): Prop :=
  match phi with
  | Lit     x
     => v M x w (* should be inhabited, i.e., true *)
  | Box     psi
     => forall w': W (F M), R (F M) w w' ->
                            formula_valuation M w' psi
  | Dia     psi
     => exists w': W (F M), R (F M) w w' /\
                            formula_valuation M w' psi
  (* some code omitted *)
  end.
\end{minted}
In order to ease the task of writing formulas and its semantics properties, we
define Coq notations that mimics the standard way of writing them.

@@

>>>>

Before defining the Kripke semantics, we need to represent the model used to
interpret a modal logic formula. We encode a frame by a record formed by
a type \mintinline{coq}{W: Set} to represent the set of worlds and an
accessibility relation denoted by a type \mintinline{coq}{R: W -> W -> Prop}.
\begin{minted}{coq}
Record Frame: Type := {
  W: Set;
  R: W -> W -> Prop;
}.
\end{minted}
A model is then denoted by another record, formed by a frame and a labeling function,
which assign the truth value of a variable at a given world.
\begin{minted}{coq}
Record Model: Type := {
  F: Frame; 
  v: nat -> (W F) -> Prop; 
}.
\end{minted}
Note that the type of the labeling function \mintinline{coq}{v} ensures that it
refers to a world from the set of possible worlds in the frame
\mintinline{coq}{F}\footnote{We recall that \mintinline{coq}{W F} is Coq's syntax for
accessing field \mintinline{coq}{W} from the record \mintinline{coq}{F}.}. The encoding of the Kripke semantics is done by a Coq function
that implements the relation of Figure~\ref{fig:kripke}. We omit the code
for propositional logics connectives for brevity. The interesting parts are for
variables (constructor \mintinline{coq}{Lit}) which uses the labeling function
\mintinline{coq}{v} from the model \mintinline{coq}{M}. The meaning of
modalities $\Box$ and $\Diamond$ are represented by a quantifying over worlds
using the accessibility relation $R$. 
\begin{minted}{coq}
Fixpoint formula_valuation (M: Model) (w: W (F M))
                                 (phi: form): Prop :=
  match phi with
  | Lit     x
     => v M x w (* should be inhabited, i.e., true *)
  | Box     psi
     => forall w': W (F M), R (F M) w w' ->
                            formula_valuation M w' psi
  | Dia     psi
     => exists w': W (F M), R (F M) w w' /\
                            formula_valuation M w' psi
  (* some code omitted *)
  end.
\end{minted}
In order to ease the task of writing formulas and its semantics properties, we
define Coq notations that mimics the standard way of writing them.

@@

\begin{acks}
  The present work was supported by Fundação de Amparo à Pesquisa de Minas
  Gerais (FAPEMIG) under grant APQ-01683-21 and Fundação de Amparo à Pesquisa de
  Santa Catarina (FAPESC) under grant 2021TR961.
\end{acks}
